\clearpage
{
\vspace{-1cm}
\begin{center}
\textit{\large \color{oxfordblue} Acknowledgments}
\end{center}}
This thesis is the result of a long and transformative process, in which many people played a crucial role in supporting either the work or the author through the numeros hazards that arose. The aim of this preface is to express my deepest gratitude to everyone it concerns. \\

For her insigtful and generous support, I want to warmly \textit{ringraziare} my supervisor Daniela Borteletto. Her insistance in my going to CERN has been one of the most impactful recommendation in my life, and there is not a single day I regret having followed her advice.\\

Throughout my DPhil, I have had the chance to interact with remarkable individuals whose dedication to their field has left a deep impression in me. I want to first and foremost say \textit{Danke schön} to Elisabeth Schopf, for her brillant support through the work on the analysis. She has been one of the core driver of the effort on this project through her unwavering motivation and profound knowledge of every dark corner of this massive analysis. \textit{Danke} also to Maria Mironova for her help early in my DPhil, as well as her awesome thesis that completely deserved the ATLAS prize and greatly helped me make sense of it all. Finally, cheers to Oxford ATLAS group for the great atmosphere in the DWB building and the many interesting presentations. \\

From outside of Oxford, I want to thank the Flavour Tagging group of ATLAS for the great collaboration and the awesome progress realised. I particularly want to express my \textit{Dankbarkeit} to Philipp Gadow for his entirely contagious enthousiasm and his ability to get things done - ATLAS is lucky to have him. I also want to thank Nicole Hartman and Samuel Van Stroud for nudging me towards the hyperparameter optimisation of GN2 with $\mu$$P$ and their great support. A huge thanks also to the \vhbc\ analysis team for the tremendous collaboration. \\

I could not continue this preface further without taking a detour to thank my many awesome friends. They have provided the best environment possible to lose my hair. \textit{Merci} to the Belgian and French teams, \textit{thank} you to the English one, \textit{sláinte} to the Irish roommate, \textit{grazie} to my college bestie. \textit{Grazie} also to Antonino Zichichi for welcoming us to his unforgettable office. \\

\noindent\textit{Grazie mille per tutto, Alice.}\\
\noindent\textit{Tutto quello che ho da dirti,}\\
\noindent\textit{spero che te lo farò capire}\\
\noindent\textit{attraverso le mie azioni,}\\
\noindent\textit{senza parole.} \\

To conclude with the essential, \textit{merci} to my family. To the present ones, your support and kindness is the warmth that keeps my resolve going. To the absent one, your memory lives on and these pages are dedicated to you. My desire to study physics in Oxford was born in your presence, and this long journey has finally reached its destination. \\
\begin{center}
\textit{\color{oxfordblue} Tapadh leibh}
\end{center}